GlasSees - Providing Context Menus for the Real World Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/targeting.tex
add error rate

@@

Error rates were low in both conditions (\bjoern{enter number of user errors in each condition}), precluding us from running a more detailed analysis.

>>>>

Error rates were low in both conditions (1.1\% in {\em infrared} condition, and 2.9\% in {\em list} condition), precluding us from running a more detailed analysis.

@@
